Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-11-22 Ben_Manuscripts/structure_paper/Outline.tex
Added bibtex file and compiled pdf
updates to outline and debugging

  R-spots, which appears in both simulated XRD patterns, is a result of the way 
  alkane tails pack together.
  \begin{itemize}
  	\item Previously, the spots in the diffraction pattern had been explained 
	as the product of tilted alkane chains. % BJC: reference 2014 ACS nano paper
	\item We measured the tilt angle of the alkane chains and showed that our 
	system equilibrates to an average tilt angle close to zero degrees ~\ref{fig:tilt} % Could belong in supplemental. Leaving here for now 
	\item To understand the origin of the spots, we determined which atoms gave rise to the feature
	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
        that the spots arise as a consequence of the tails. 
	\item By removing atoms from the trajectory and simulating a diffraction 
	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails}).
	\item Since the tails stay nearly flat, we plotted the centroids of the 
	tails and measured the angle between each centroid and its nearest neighbors
	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
	\item We see distinct peaks in the distribution of these angles (Figure~\ref{fig:tail_packing})
  \end{itemize}

@@

  The peaks in the tilt angle distribution are consistent with the location of R-spots.
  \begin{itemize}
	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
	of spots are located on the simulated patterns (See Supplemental Information for quantitative proof)
	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
        and found the angle at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which 
        is a reconcilable difference with our simulated results.  
  \end{itemize}

@@

  \begin{figure}
  \centering
  	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
        		\centering
        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
        		\caption{}~\label{fig:offset_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
		\centering
	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
		        \caption{}~\label{fig:layered_tails}
		\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
	        \centering
		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
		        \caption{}~\label{fig:rz_layered}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
        	\centering
		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
		        \caption{}~\label{fig:test}
		\end{subfigure}
	\end{subfigure}
  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
  same peaks are visible when the 2D simulated diffraction data is radially integrate in the R-alkanes region,
  (b) and (d) respectively.}~\label{fig:tail_packing}
  \end{figure}

@@

  Water is not needed to obtain and simulate the correct equilibrium 
  membrane structure.
  \begin{itemize}
	\item We note that water absorbed during membrane synthesis may
        be present in far lower concentrations than those 
        tested here.
	\item We do not eliminate the possibility that water is necessary
        in order to drive self-assembly. Studying the mechanisms of self assembly is
	beyond the scope of this work.
	\item However, once the system has formed the Col\textsubscript{h} 
	phase, adding water only creates disorder in the structure
	\item In the equilibrium configuration, if water exists, it is confined
	to the pore region where there is no driving force for aggregation of 
	water molecules. 
	\item The packing of water molecules will be too sparse to form a 
	hydrogen bonding network.
  \end{itemize}

@@

  We use the equilibrated parallel displaced system to calculate ionic 
  conductivity since its structure is the closest match to experiment.
  The model gives reasonable estimates of ionic conductivity when compared to 
  experiment.
  \begin{itemize}
  	\item Calculated values of ionic conductivity obtained using the Nernst 
	Einstein relation and Collective Diffusion model are compared in 
	Figure~\ref{fig:conductivity}.
	\item The two methods agree with each other within error, although the 
	uncertainty obtained using the Collective Diffusion model is much higher.
	\item Much longer simulations are needed to lower the uncertainty, however it
	is unfeasible to do so with large model. 
	\item For this reason we will likely only use the Nernst Einstein relation
	in future calculations of this type. 
  \end{itemize}

@@

  We applied the crosslinking algorithm to the equilibrated parallel-displaced  
  configuration with 5 monomers per layer.
  \begin{itemize}  %BJC: working on the following. The following is what I expect
  	\item There is an even distribution of crosslinks between same monomer tails, 
	between monomers in the same pore and between monomers in different pores 
	including periodic boundaries.  % BJC: might leave this detail in the supplemental
	\item We reach 95 \% conversion of terminal vinyl groups % BJC: we'll see
	\item The distance between pores shrinks by 1 \angstrom~ after the system is 
	crosslinked  % probably smaller
	\item We simulated the crosslinked simulations in the NPT ensemble for 100 ns
	\item Major features are still present in the X-ray diffraction ~\ref{fig:rzplot_xlink} % BJC: maybe
	\item The ionic conductivity is higher/lower in the crosslinked system ~\ref{fig:ic_xlink} % BJC: Nernst-Einstein is lower. Need a longer simulation to check Collective-Diffusion 
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[widht=\textwidth]{rzplot_xlink.png}
	\caption{}~\label{fig:rzplot_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{ic_xlink.png}
	\caption{}~\label{fig:ic_xlink}
  \end{subfigure}
  \caption{(a) Reflections produced by the crosslinked configuration fade relative
  to the uncrosslinked system. The colorbar shown is the same used for the uncrosslinked
  system. (b) The ionic conductivity is smaller relative to the uncrosslinked system, but
  still much larger than the experimental value}~\label{fig:xlink}
  \end{figure}

>>>>

  R-spots, which appears in both simulated XRD patterns, is a result of the way 
  alkane tails pack together.
  \begin{itemize}
  	\item Previously, the spots in the diffraction pattern had been explained 
	as the product of tilted alkane chains. % BJC: reference 2014 ACS nano paper
	\item We measured the tilt angle of the alkane chains and showed that our 
	system equilibrates to an average tilt angle close to zero degrees ~\ref{fig:tilt} % Could belong in supplemental. Leaving here for now 
	\item To understand the origin of the spots, we determined which atoms gave rise to the feature
	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
        that the spots arise as a consequence of the tails. 
	\item By removing atoms from the trajectory and simulating a diffraction 
	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails}).
	\item Since the tails stay nearly flat, we plotted the centroids of the 
	tails and measured the angle between each centroid and its nearest neighbors
	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).  %BJC: at one point Matt mention doing a correlation function instead of just measuring the angles
	\item We see distinct peaks in the distribution of these angles (Figure~\ref{fig:tail_packing})
  \end{itemize}

@@

  The peaks in the tilt angle distribution are consistent with the location of R-spots.
  \begin{itemize}
	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
	of spots are located on the simulated patterns
	\item We confirmed this conclusion by radially integrating the 2D WAXS pattern for q values
	between 1.57 and 1.4 (real space between 4 and 4.5 \AA) 
	\item We observe that distinct peaks appear c.a. 30 $\degree$, in close agreement with the
	previously measured angle distribution (~\ref{fig:offset_integration}~\ref{fig:layered_integration})
%	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
	\item We performed the same integration on the raw experimental data and found the angle
	at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which is a 
	reconcilable difference with our simulated results.  
  \end{itemize}

@@

  \begin{figure}
  \centering
  	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
        		\centering
        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
        		\caption{}~\label{fig:offset_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
		\centering
	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
		        \caption{}~\label{fig:offset_integration}
		\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
	        \centering
		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
		        \caption{}~\label{fig:rz_layered}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
        	\centering
		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
		        \caption{}~\label{fig:layered_integration}
		\end{subfigure}
	\end{subfigure}
  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
  same peaks are visible when the 2D simulated diffraction data is radially integrated in the R-alkanes region,
  (b) and (d) respectively.}~\label{fig:tail_packing}
  \end{figure}

@@

  Water is not needed to obtain and simulate the correct equilibrium 
  membrane structure.
  \begin{itemize}
	\item We note that water absorbed during membrane synthesis may
        be present in far lower concentrations than those 
        tested here.
	\item We do not eliminate the possibility that water is necessary
        in order to drive self-assembly. Studying the mechanisms of self assembly is
	beyond the scope of this work.
	\item However, once the system has formed the Col\textsubscript{h} 
	phase, adding water only drives disorder in the structure
	\item In the equilibrium configuration, if water exists, it is confined
	to the pore region where there is no driving force for aggregation of 
	water molecules. 
	\item In the case of trace water, water molecules will be too sparse to
	form a hydrogen bonding network.
  \end{itemize}

@@

  We use the equilibrated parallel displaced system to calculate ionic 
  conductivity since its structure is the closest match to experiment.
  The model gives reasonable estimates of ionic conductivity when compared to 
  experiment.
  \begin{itemize}
  	\item Calculated values of ionic conductivity obtained using the Nernst 
	Einstein relation and Collective Diffusion model are compared in 
	Figure~\ref{fig:conductivity}.
	\item The two methods agree with each other within error, although the 
	uncertainty obtained using the Collective Diffusion model is much higher.
	\item Much longer simulations are needed to lower the uncertainty, however it
	is not feasible to do so with a large model. 
	\item For this reason we will likely only use the Nernst Einstein relation
	in future calculations of this type. 
  \end{itemize}

@@

  We applied the crosslinking algorithm to the equilibrated parallel-displaced  
  configuration with 5 monomers per layer.
  \begin{itemize}  %BJC: working on the following. The following is what I expect
%  	\item There is an even distribution of crosslinks between same monomer tails, 
%	between monomers in the same pore and between monomers in different pores 
%	including periodic boundaries.  % BJC: might leave this detail in the supplemental
	\item We reach 95 \% conversion of terminal vinyl groups % BJC: we'll see
	\item The distance between pores shrinks by 0.4\angstrom~ after the system is 
	crosslinked  
	\item We simulated the crosslinked system in the NPT ensemble for 100 ns
	\item Major features are still present in the X-ray diffraction, however at lower intensities ~\ref{fig:rzplot_xlink} 
	\item The ionic conductivity is lower in the crosslinked system ~\ref{fig:ic_xlink} % BJC: Nernst-Einstein is lower. Need a longer simulation to check Collective-Diffusion - I can probably avoid that by saying that we will be sticking with the Nernst-Einstein method
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{rzplot_xlink.png}
	\caption{}~\label{fig:rzplot_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{ic_xlink.png}
	\caption{}~\label{fig:ic_xlink}
  \end{subfigure}
  \caption{(a) Reflections produced by the crosslinked configuration fade relative
  to the uncrosslinked system. The colorbar shown is the same used for the uncrosslinked
  system. (b) The ionic conductivity is smaller relative to the uncrosslinked system, but
  still much larger than the experimental value}~\label{fig:xlink}
  \end{figure}
